---
title: "Introduction to CDREGM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to CDREGM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

**CDREGM** provides tools for estimating economic growth models within the
*Capitalism, Democracy, and Rule of Law* (CDR) framework.  The central
premise is that institutional quality — measured along three dimensions —
is a first-order determinant of long-run per-capita income growth.

| Dimension        | Typical proxy variables                          |
|------------------|--------------------------------------------------|
| Capitalism       | Property-rights index, economic-freedom score    |
| Democracy        | Polity IV, Freedom House political-rights score  |
| Rule of Law      | World Governance Indicators, ICRG law & order    |

## Basic usage

```{r basic}
library(CDREGM)

set.seed(42)
n <- 100
df <- data.frame(
  growth      = rnorm(n, 2, 1.5),
  prop_rights = runif(n, 0, 10),
  democracy   = runif(n, 0, 10),
  rule_of_law = runif(n, 0, 10),
  ln_gdp0     = rnorm(n, 8, 1)
)

m <- cdr_growth(
  data       = df,
  gdp_growth = "growth",
  cdr_vars   = c("prop_rights", "democracy", "rule_of_law"),
  controls   = "ln_gdp0"
)

summary(m$fit)
```

## Interpreting coefficients

A positive coefficient on a CDR variable indicates that higher institutional
quality is associated with faster growth, holding other factors constant.
Consult the vignette `vignette("panel-data", package = "CDREGM")` (planned)
for fixed-effects and GMM extensions.
```
