---
title: "Introduction to CDREGM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to CDREGM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## The CDR framework

**CDREGM** implements the *Capitalism, Democracy, and Rule of Law* (CDR)
growth model of Ridley and co-authors. Three standardized institutional
variables --- capitalism `C` (market capitalization), democracy `D`
(V-Dem electoral democracy), and rule of law `R` (control of corruption)
--- together with natural resources `N` and, as an instrument, absolute
latitude `L`, explain cross-country differences in growth. The model
carries an interaction term `C * D * R` whose negative coefficient is
read as *democratic friction*: the cost of decision-making disagreement
when all three institutions are strong at once.

```{r pkg}
library(CDREGM)
```

## Building the panel

`cdr_build_panel()` merges the bundled `indicators` and `countries`
datasets and adds the min-max standardized columns used throughout.

```{r panel}
panel <- cdr_build_panel()
head(panel[, c("iso2c", "year", "C_std", "D_std", "R_std", "CDR")])
```

## Estimating the model

```{r ols}
m <- cdr_ols(panel)
m
```

`cdr_index()` ranks countries by the friction-adjusted composite index:

```{r index}
head(cdr_index(panel))
```

## Structural quantities

The parametric endogenous growth rate and the theoretical growth ceiling
reproduce the published values when the paper's coefficients are used:

```{r endog}
cdr_endogenous_rate(coefficients = "published")
```

## Policy tools

```{r policy}
head(cdr_growth_gap(panel))

cdr_simulate("Poland", c(R_std = 0.1), data = panel, n_rep = 200, seed = 1)
```

## Diagnostics and reporting

```{r diag}
cdr_diagnostic_suite(panel)

cdr_explain_model(m)
```

Further tools cover panel and GMM estimation (`cdr_panel()`,
`cdr_gmm()`), quantile and Bayesian regression (`cdr_quantile()`,
`cdr_bayes()`), spatial dependence (`cdr_spatial()`), visualization
(`cdr_plot_3d()`, `cdr_plot_map()`), an interactive explorer
(`cdr_explorer()`), and data maintenance (`cdr_update_data()`,
`cdr_historical_panel()`).
