---
title: "`r paste0('CDR Country Profile: ', params$country)`"
date: "`r Sys.Date()`"
output: html_document
params:
  country: "US"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(CDREGM)
panel <- cdr_build_panel()
cs    <- CDREGM:::.cross_section(panel)
iso   <- params$country
row   <- cs[cs$iso2c == iso, ]
name  <- row$country
```

## `r name` (`r iso`)

```{r overview}
idx <- cdr_index(panel)
rank <- match(iso, idx$iso2c)
knitr::kable(
  data.frame(
    Metric = c("Capitalism (C)", "Democracy (D)", "Rule of law (R)",
               "CDR interaction", "Growth rate g", "CDR index rank"),
    Value  = c(round(row$C_std, 3), round(row$D_std, 3), round(row$R_std, 3),
               round(row$CDR, 3), round(row$g, 4),
               paste0(rank, " / ", nrow(idx)))
  )
)
```

## Peer group

```{r peers}
knitr::kable(as.data.frame(cdr_peer_group(iso, k = 6, data = panel)),
             digits = 3)
```

## Growth gap from the CDR frontier

```{r gap}
gap <- cdr_growth_gap(panel)
knitr::kable(as.data.frame(gap[gap$iso2c == iso, ]), digits = 3, row.names = FALSE)
```

The `priority` column names the single reform with the largest growth
payoff at current values of the other two variables.

## Democratic friction

```{r friction}
fr <- cdr_democratic_friction(panel)
knitr::kable(as.data.frame(fr[fr$iso2c == iso, ]), digits = 4, row.names = FALSE)
```

`friction_growth` is the cost of the `C * D * R` decision-making term;
`net_institutional` shows democracy and rule of law remain net positive
once that cost is subtracted.

---

*Generated by `CDREGM::cdr_country_report()`.*
